---
title: "Examining Multiples"
author: "DC"
date: "Saturday, May 16, 2015"
output:
  html_document:
    theme: readable
runtime: shiny
---

#Overview

The following are some interactive charts to examine the historical and current trend of EBITDA, CPS, and EPS multiples for PKD and its peers.
In each section, the line chart represents the historical rolling (Price or EV) over the Next Twelve Months _(NTM)_ of estimates.  

### The Company selecter
On the above right is a dropbox to select the performance of PKD and several of its peers

### The Line Chart
Click and drag on this chart to select a window of time to be represented on the boxplot _(to right)_ and histogram _(below)_
Use the slider beneath the time series chart to move the selected periodicity through time.
Double click the chart to reset the zoom level

### The BoxPlot
To the right of the line chart is a Boxplot for the time series information in the line chart.  
The Median value is represented by the bold line in the middle of the box and indicated by the blue number
The upper and lower quartiles are represented by the edges of the box.
Dots represent outliers

### The Histogram
Below the line chart are dynamic histgrams, which update according to the data currently visible in the line chart.
This illustrates the distribution of the multiples, and provide a more complete understanding than a median or mean number alone.



#EV/EBITDA Multiples

```{r, echo=FALSE, message=FALSE, warning=FALSE}
load("./rawDF.RData")
source("./ts_widget.R")
tsExplore(raw, gmin = 3, gmax = 10)

```


#P/E multiples
_Note that earnings for oil service companys are frequently low or negative, making historical trend analysis of multiples difficult. A more representative analysis would involve earnings yield, which is available_
```{r, echo=FALSE, message=FALSE, warning= FALSE}
load("./PE_TS.RData")

tsExplore(PE_TS)

```

#P/CPS Mutliples
```{r, echo=FALSE, message=FALSE, warning= FALSE}
load("./CF_TS.RData")

tsExplore(CF_TS)

```




